Machine learning high multiplicity matrix elements for electron-positron and hadron-hadron colliders

### 2023-03-13 conclusion.tex
change madloop to madgraph

The success of this approach prompted the study of applying
the factorisation-aware model to emulate the more expensive
one-loop matrix elements for the same family of processes,
as seen in Chapter~\ref{chapter:fame2}.
It was found that by adapting the
Catani-Seymour dipole functions to the more relevant antenna functions
containing one-loop singular behaviour, the
accurate emulation of NLO QCD k-factors was achieved.
In this study we also demonstrated that it was possible
for the emulator to learn the renormalisation scale dependence
of the one-loop matrix elements, allowing it to be used to
carry out scale variations.
We showed that $e^{+}e^{-} \rightarrow q \bar{q} ggg$ NLO k-factors
could be predicted with accuracy at the 1\% level, representing a speed up in
evaluation of over 3 orders of magnitude compared to {\MadLoop} on
a single CPU core.

>>>>

The success of this approach prompted the study of applying
the factorisation-aware model to emulate the more expensive
one-loop matrix elements for the same family of processes,
as seen in Chapter~\ref{chapter:fame2}.
It was found that by adapting the
Catani-Seymour dipole functions to the more relevant antenna functions
containing one-loop singular behaviour, the
accurate emulation of NLO QCD k-factors was achieved.
In this study we also demonstrated that it was possible
for the emulator to learn the renormalisation scale dependence
of the one-loop matrix elements, allowing it to be used to
carry out scale variations.
We showed that $e^{+}e^{-} \rightarrow q \bar{q} ggg$ NLO k-factors
could be predicted with accuracy at the 1\% level, representing a speed up in
evaluation of over 3 orders of magnitude compared to {\MadGraph} on
a single CPU core.
